Species persistence under climate and fishing

### 2014-02-01 Writing/MS.tex
Adding explanation about age structure, close #21

We also did not include age structure in our model. The effects of both harvesting and climate change may be different across different age classes; including this level of complexity is left for future work. Additionally, we did not include any mechanisms aside from larval dispersal by which the population could keep up with a shifting climate.  In addition to these species-specific extensions, this modeling framework could be extended to consider species interactions, especially predator-prey pairs.  By introducing a predatory species, we would be imposing yet another stressor on the focus species \citep{Lingetal2009, Gurevitchetal2000} and we are interested in measuring the interaction between the effects of this stressor and the two we consider here.

@@

\section{ Acknowledgements}
We'd like to thank our reviewers for providing constructive comments.

>>>>

We also did not include age structure in our model. The effects of both harvesting and climate change may be different across different age classes which may cause long-term changes in abundance or increased variance due to cohort resonance \citep{Botsfordetal2011, Rouyeretal2012}. Both of these effects can be expected to reduce population viability in the face of both fishing and range shifts; including this level of complexity is left for future work. Additionally, we did not allow any mechanisms aside from larval dispersal by which the population could keep up with a shifting climate.  In addition to these species-specific extensions, this modeling framework could be extended to consider species interactions, especially predator-prey pairs.  By introducing a predatory species, we would be imposing yet another stressor on the focus species \citep{Lingetal2009, Gurevitchetal2000} and we are interested in measuring the interaction between the effects of this stressor and the two we consider here.

@@

\section*{ Acknowledgements}
We'd like to thank our reviewers for providing constructive comments.
